Modeling defoliation of Pinus Radiata trees using hyperspectral remote sensing data

### 2018-07-31 01_writing/Schratz_hyperspectral.tex
complete table with performances

% Performance estimates
\begin{table}[b!]
\centering
\caption[t]{Four-fold spatial \ac{CV} performances of RR, SVM and xgboost using \ac{RMSE} as the error measure.
	Mean and standard deviation are shown.}
\begingroup\footnotesize
\begin{tabular}{llll}
	RR            & SVM           & xgboost       \\
	\hline
	59.10 (22.71) & 36.23 (15.73) & 33.26 (16.61) \\
	\bottomrule
\end{tabular}
\endgroup
\label{tab:penalty_comparison}
\end{table}

\begin{table}[t!]
\centering
\caption[t]{Predictive performance of \textit{xgboost} using all observations (All Observations ) and observations from single plots only (Single Plot Observations) with \ac{RMSE} as the error measure. The performance estimates for "All Observations" correspond to the fold for which the respective plot was serving as the test set. Column "single plot", shows the mean performances at the repetition level of a SpCV (5 folds, 5 repetitions), scored by using data of the respective plot only.}
\begingroup\footnotesize
\begin{tabular}{lll}
	\\
	Plot/Data & All Observations (Block CV) & Single Plot Observations (SpCV) \\
	\hline
	Laukiz 1  & 22.03                       & -                               \\
	Laukiz 2  & 51.75                       & 17.37  (update to rep mean!)    \\
	Luiando   & 13.20                       & -                               \\
	Oiartzun  & 32.97                       & 14.72    (update to rep mean!)  \\
	\bottomrule
\end{tabular}
\endgroup
\label{tab:supermodel_performance}
\end{table}

>>>>

% Performance estimates
\begin{table}[t!]
\centering
\caption[t]{Four-fold block spatial \ac{CV} performances of RR, SVM and xgboost using \ac{RMSE} as the error measure.
	Mean and standard deviation are shown.}
\begingroup\footnotesize
\begin{tabular}{llll}
	RR            & SVM           & xgboost       \\
	\hline
	59.10 (22.71) & 36.23 (15.73) & 33.26 (16.61) \\
	\bottomrule
\end{tabular}
\endgroup
\label{tab:penalty_comparison}
\end{table}

\begin{table}[b!]
\centering
\caption[t]{Predictive performance of \textit{xgboost} using all observations (All Observations) and observations from specific plots only (Single Plot Observations) with \ac{RMSE} as the error measure. The performance estimates for "All Observations" correspond to the fold for which the respective plot was serving as the test set. Column "Single Plot Observations", shows the mean performances at the repetition level of a spatial CV (5 folds, 5 repetitions), scored by using data of the respective plot only.}
\begingroup\footnotesize
\begin{tabular}{lll}
	\\
	Plot/Data & All Observations (Block CV) & Single Plot Observations (SpCV) \\
	\hline
	Laukiz 1  & 22.03                       & 19.18                               \\
	Laukiz 2  & 51.75                       & 17.24      \\
	Luiando   & 13.20                       & 8.30                             \\
	Oiartzun  & 32.97                       & 14.40      \\
	\bottomrule
\end{tabular}
\endgroup
\label{tab:supermodel_performance}
\end{table}
